---
title: "R Notebook"
output:
  pdf_document: default
  html_notebook: default
---

import necessary libraries and data

```{r}
library(lme4)
library(nlme)
library(tidyr)
library(ggplot2)
library(GGally)
library(psych)
library(corrplot)
library(MASS)
library(gpairs)
library(car)
library(rmeta)
library(dplyr)
library(purrr)
library(moments) # to calculate skewness 

```

## contrast coding

We use contrast coding to get a useful, nice-to-interpret intercept in our model.
We want the intercept to be equivalent to the "mean of all subjects from all studies".
With usual coding of the factor "Study", the overall intercept of the model would be equvalent to the mean of study #1.
Therefore, we create artificial variables according to: https://pagepiccinini.com/2016/03/18/contrast-coding-with-three-level-variables/
For two variables, contrast coding is straightforward.
For three variables, keep in mind, that interpretation of some other model parameters may change (c.f. website above).


```{r}


#' Contrast coding for HLM
#'
#' We use contrast coding to get a useful, nice-to-interpret intercept in our model. 
#' We want the intercept to be equivalent to the "mean of all subjects from all studies".
#' With usual coding of the factor "Study", the overall intercept of the model would be equvalent to the mean of study #1.
#' does a keyword search over the headers to find those column headers that
#' match a particular keyword, e.g., mean, median, etc.
#' Therefore, we create artificial variables according to: https://pagepiccinini.com/2016/03/18/contrast-coding-with-three-level-variables/
#' For two variables, contrast coding is straightforward.
#' For three variables, keep in mind, that interpretation of some other model parameters may change (c.f. website above).
#' 
#' @param df a data frame object.
#' @param colName The name of the column (char) that shall be contrast coded.
#' @param numLevels Number of levels for contast coding (int). Only 2, 3 or 4 possible. Defaults to 2.
#' @param interceptCorrect 
#'
#' @return A data frame object containing the dummy coded variable.
#' @export
contrastCoding <- function(df, colName, numLevels = 2, interceptCorrect = TRUE){
  require(dplyr)
  # change the colname for convenience
  names(df)[names(df) == colName] <- "V1"
  
  w1A <- -0.5  #nb / nab # weight of contrast 1, group A
  w1B <-  0.5  #na / nab
  
  # in any case, calculate A vs B
  df = df %>%
    mutate(contrast_AvB = ifelse(V1 == 0, w1A, ifelse(V1 == 1, w1B, 0)))
  # if only 2 levels, calculate A vs C
  if ( numLevels == 2 ){
    df = df %>% 
      mutate(contrast_AvC = ifelse(V1 == 0, -0.5, ifelse(V1 == 1, 0.5, 0))) # ??? wrong ?
  
    # if 3 levels
  } else if (numLevels == 3){
    w2A <- -0.25 #nb / nabcc
    w2B <- -0.25 #na / nabcc
    w2C <-  0.5  #2 * nc / nabcc
    # if the intercept is supposed to be meaningful
    if ( interceptCorrect == TRUE ){
      df = df %>%
        mutate(contrast_ABvC = ifelse(V1 == 2, w2C, ifelse(V1 == 0, w2A, w2B)))
    } else{
      # if the intercept is not supposed to be meaningful, but the differences between studies
      df = df %>%
        mutate(contrast_ABvC = ifelse(V1 == 2, 0.5, -0.5)) # do not use this version already
    }
  
    # if 4 levels
  } else if (numLevels == 4){
    # von v3
    w2A <- -0.25 #nb / nabcc
    w2B <- -0.25 #na / nabcc
    w2C <-  0.5  #2 * nc / nabcc
    # if the intercept is supposed to be meaningful
    if ( interceptCorrect == TRUE ){
      df = df %>%
        mutate(contrast_ABvC = ifelse(V1 == 2, w2C, ifelse(V1 == 0, w2A, w2B)))
    } else{
      # if the intercept is not supposed to be meaningful, but the differences between studies
      df = df %>%
        mutate(contrast_ABvC = ifelse(V1 == 2, 0.5, -0.5)) # do not use this version already
    }

    w3A <- -0.5/3 #nb / nabcddd
    w3B <- -0.5/3 #na / nabcddd
    w3C <- -0.5/3 #
    w3D <-  0.5   #3 * nd / nabcddd
    # if the intercept is supposed to be meaningful
    if ( interceptCorrect == TRUE ){
      df = df %>%
        mutate(contrast_ABCvD = ifelse(V1 == 3, w3D, ifelse(V1 == 2, w3C, ifelse(V1 == 1, w3B, w3A))))
    } else{
      # if the intercept is not supposed to be meaningful, but the differences between studies
      df = df %>%
        mutate(contrast_ABvC = ifelse(V1 == 2, 0.5, -0.5)) # not yet finished this version !!
    }
  }
  
  # change the colname back to its original
  names(df)[names(df) == "V1"] <- colName
  
  return(df)
}


# for Hormone contrast

#' Contrast coding for HLM
#'
#' We use contrast coding to get a useful, nice-to-interpret intercept in our model. 
#' We want the intercept to be equivalent to the "mean of all subjects from all studies".
#' With usual coding of the factor "Study", the overall intercept of the model would be equvalent to the mean of study #1.
#' does a keyword search over the headers to find those column headers that
#' match a particular keyword, e.g., mean, median, etc.
#' Therefore, we create artificial variables according to: https://pagepiccinini.com/2016/03/18/contrast-coding-with-three-level-variables/
#' For two variables, contrast coding is straightforward.
#' For three variables, keep in mind, that interpretation of some other model parameters may change (c.f. website above).
#' 
#' @param df a data frame object.
#' @param colName The name of the column (char) that shall be contrast coded.
#' @param numLevels Number of levels for contast coding (int). Only 2, 3 or 4 possible. Defaults to 2.
#' @param interceptCorrect 
#'
#' @return A data frame object containing the dummy coded variable.
#' @export
contrastCodingHormone <- function(df, colName, numLevels = 2, interceptCorrect = TRUE){
  require(dplyr)
  # change the colname for convenience
  names(df)[names(df) == colName] <- "V1"
  
  w1A <- -0.5  #nb / nab # weight of contrast 1, group A
  w1B <-  0.5  #na / nab
  
  # in any case, calculate A vs B
  df = df %>%
    mutate(contrast_MvP = ifelse(Study == 2, ifelse(V1 == 0, w1A, w1B), 0))

  # change the colname back to its original
  names(df)[names(df) == "V1"] <- colName
  
  return(df)
}




```


# now loop over all data

## load data 

```{r}
library(R.matlab)
dfEFP <- readMat("/Users/roman/projects/coreSysRev/parameters/parameters_EFP_fairhallishai.mat")
dfFEM <- readMat("/Users/roman/projects/coreSysRev/parameters/parameters_femfear_fairhallishai.mat")
dfCYM <- readMat("/Users/roman/projects/coreSysRev/parameters/parameters_cycla_AM_fairhallishai.mat")
dfCYP <- readMat("/Users/roman/projects/coreSysRev/parameters/parameters_cycla_AP_fairhallishai.mat")
dfWaH <- readMat("/Users/roman/projects/coreSysRev/parameters/parameters_WakemanHanson_fairhallishai.mat")

subNumEFP <- seq(1,23)
subNumFEM <- seq(24,50)
subNumCYM <- c(51, 52, 53, 54,     56, 57, 58, 59, 60, 61,     63, 64, 65, 66, 67, 68)
subNumCYP <- c(51, 52, 53, 54, 55, 56, 57, 58, 59, 60, 61, 62, 63, 64, 65,     67, 68)
subNumWaH <- c(69,69,69,69,69,69,69,70,70,70,70,70,70,70,71,71,71,71,71,71,72,72,72,72,72,72,72,73,73,73,73,73,73,73,73,74,74,74,74,74,74,74,74,74,75,75,75,75,75,75,75,75,76,76,76,76,76,76,77,77,77,77,77,77,77,77,77,78,78,78,78,78,78,78,78,79,79,79,79,79,79,79,79,80,80,80,80,80,81,81,81,81,81,81,81,81,82,82,82,82,82,82,82,82,82,83,83,83,83,83,83,83,83,83,84,84,84,84,84,84,84,84,84)

Subject <- c(subNumEFP, subNumFEM, subNumCYM, subNumCYP, subNumWaH)
Study <- c(rep(0,23),rep(1,27), rep(2,16+17), rep(3,123))
Hormone <-  c(rep(0,23+27+16), rep(1,17), rep(0,123))

# some overall parameters

thres <- 0.05 / 6 # threshold for multiple comparisons
nonSigValue <- 0 # the value that is inserted if a connection is non-significant
colorRange <- c(-1.5,1.5)

```








```{r}


```




## B matrix: effect of faces

### loop this over parameter

```{r}
# table for results
facesIntercept <- matrix(NA, 3, 3)
facesPVal      <- matrix(NA, 3, 3)
dfResults <- data.frame(Source=numeric(0), Target=numeric(0), Matrix=character(0), Type=character(0), Value=numeric(0), stringsAsFactors=FALSE)

regionNames = c("OFA","FFA","STS")
bigDF <- data.frame(matrix(ncol=5,nrow=0, dimnames=list(NULL, c("Subject", "Parameter", "Study", "Hormone", "Connection"))))

for ( target in 1:3 ){      # target region
  for ( source in 1:3 ){    # source region
    if (source == target){
      next # skip this iteration if it is a self connection
      
    } else {
      
      # load parameters in df
      Parameter <-      c(dfEFP$mEpsBFaces[target,source,], # DCM parameters
                          dfFEM$mEpsBFaces[target,source,],
                          dfCYM$mEpsBFaces[target,source,],
                          dfCYP$mEpsBFaces[target,source,],
                          dfWaH$mEpsBFaces[target,source,])
      Subject <- c(subNumEFP, subNumFEM, subNumCYM, subNumCYP, subNumWaH)
      Study <- c(rep(0,23),rep(1,27), rep(2,16+17), rep(3,123))
      Hormone <-  c(rep(0,23+27+16), rep(1,17), rep(0,123))
      dfFaces <- data.frame(Subject, Parameter, Study, Hormone)
      dfFaces$Subject <- as.factor(dfFaces$Subject)
      dfFaces$Study   <- as.factor(dfFaces$Study)
      dfFaces$Hormone <- as.factor(dfFaces$Hormone)
      
      # create contrasts
      dfFaces <- contrastCoding(df = dfFaces, colName = "Study", numLevels = 4, interceptCorrect = TRUE)
      
      # create hormone contrast
      dfFaces <- contrastCodingHormone(df = dfFaces, colName = "Hormone", numLevels = 2, interceptCorrect = TRUE)
      
      
      # estimate model
      m1 <- lme(Parameter ~ 1 + contrast_AvB + contrast_ABvC + contrast_ABCvD + contrast_MvP, random = ~1|Subject, data=dfFaces)
      # contrast_MvP
      
      #contrast_ABCvD
      #m1 <- lme(Parameter ~ 1 + contrast_AvB + contrast_ABvC + Hormone , random = ~1|Subject, data=dfFaces)
      
      # extract results
      intercept = m1$coefficients$fixed[1]
      p = summary(m1)$tTable[,"p-value"][1]
      facesIntercept[target,source] <- intercept
      facesPVal[target,source]      <- p
      dfResults[nrow(dfResults) + 1,] = list(source,target, "faces", "intercept", intercept )
      dfResults[nrow(dfResults) + 1,] = list(source,target, "faces", "p", p )
      if (p <= thres){
        dfResults[nrow(dfResults) + 1,] = list(source,target, "faces", "intercept_sig",paste(round(intercept,2),"*") )
      } else {
        dfResults[nrow(dfResults) + 1,] = list(source,target, "faces", "intercept_sig", paste(round(intercept,2),"") )
      }
      
      # create a name for the connection
      conName <- paste(regionNames[source],">",regionNames[target]) # collapse = ""
      dfFaces$Connection <- conName 
      bigDF <- rbind(bigDF,
                     subset(dfFaces, select = c("Subject","Parameter","Study","Hormone", "Connection")))
    }
  }
} 
print("Intercept =")
facesIntercept
print("p =")
facesPVal
```

### plot the connectivity matrix

```{r}
myTheme <- theme(
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),
    panel.background = element_rect(fill = "transparent",colour = NA),
    plot.background = element_rect(fill = "transparent",colour = NA),
    axis.text.x = element_text(color="black", size=10, face = "bold", angle=0),# x tick labels
    axis.text.y = element_text(color="black", size=10, face = "bold", angle=0),# y tick labels
    axis.title = element_text(size=12, face="italic"),
    #axis.title.y = element_text(size=12, face="bold"),
    plot.title = element_text(size=15, face="bold"),
    plot.tag = element_text(size=15, face="bold"),
    panel.border = element_blank(),
    legend.position = "none"
    )

pHLM_b_faces <- qplot(x=Source , y=Target , data=subset(dfResults, Type == "intercept"), fill=as.numeric(Value), geom="tile") +
  geom_text(data=subset(dfResults, Type == "intercept_sig"), aes(label = Value, size = 35)) +
  scale_fill_gradient2(low = "blue", mid = "white", high = "red", midpoint=0, limits=colorRange) +
  scale_x_discrete(limits=c("OFA","FFA","STS")) +
  scale_y_discrete(limits=c("OFA","FFA","STS")) +
  myTheme +
  labs(title = "B-matrix\n(faces)", x = "source region", y = "target region") + #,  tag = "B"
  coord_equal() +
  facet_grid()
pHLM_b_faces
dev.copy(png,'/Users/roman/projects/coreSysRev/plots/HLM_BFaces.png')
dev.off()
```
```{r}
head(dfResults)
```

## histo

```{r}
# New facet label names for dose variable
study.labs <- c("study A","study B","study C","study D")
names(study.labs) <- c("0", "1", "2","3")

bigDF$Connection <- as.factor(bigDF$Connection)
pHist_b_faces <- ggplot(bigDF) +
  geom_density(aes(x=Parameter), fill = "darkgray") + #, fill = Hormone) 
  #scale_fill_manual(labels = c("M", "P"), values = c("#a6cee3", "#b2df8a")) + # change Colorcode labels
  geom_vline(aes(xintercept=0)) + # vertical line at x = 0
  facet_grid(Study~Connection,
             labeller = labeller(Study = study.labs)) +
  labs(x = "parameter estimates", title = "B-matrix: faces")

pHist_b_faces
dev.copy(png,'/Users/roman/projects/coreSysRev/plots/Hist_BFaces.png')
dev.off()

```
Show overview over the BMA parameters
```{r}
bigDF %>% split(.$Study) %>% map(summary)
```


## B matrix: effect of emotions

### loop this over parameter

```{r}
# table for results
facesIntercept <- matrix(NA, 3, 3)
facesPVal      <- matrix(NA, 3, 3)
dfResults <- data.frame(Source=numeric(0), Target=numeric(0), Matrix=character(0), Type=character(0), Value=numeric(0), stringsAsFactors=FALSE)
bigDF <- data.frame(matrix(ncol=5,nrow=0, dimnames=list(NULL, c("Subject", "Parameter", "Study", "Hormone", "Connection"))))


for ( target in 1:3 ){      # target region
  for ( source in 1:3 ){    # source region
    if (source == target){
      next # skip this iteration if it is a self connection
    } else {
      
      
      Subject <- c(subNumEFP, subNumFEM)
      Study <- c(rep(0,23),rep(1,27))
      Hormone <- c(rep(0,23+27))
      # load parameters in df
      Parameter <-      c(dfEFP$mEpsBEmotions[target,source,], # DCM parameters
                          dfFEM$mEpsBEmotions[target,source,])
      dfFaces <- data.frame(Subject, Parameter, Study, Hormone)
      dfFaces$Subject <- as.factor(dfFaces$Subject)
      dfFaces$Study   <- as.factor(dfFaces$Study)
      dfFaces$Hormone <- as.factor(dfFaces$Hormone)

      # create contrasts
      dfFaces <- contrastCoding(df = dfFaces, colName = "Study", numLevels = 2, interceptCorrect = TRUE)
      
      ## create hormone contrast
      #dfFaces <- contrastCodingHormone(df = dfFaces, colName = "Hormone", numLevels = 2, interceptCorrect = TRUE)
      
      # estimate model
      m1 <- lme(Parameter ~ 1 + contrast_AvB, random = ~1|Subject, data=dfFaces)

      # extract results
      intercept = m1$coefficients$fixed[1]
      p = summary(m1)$tTable[,"p-value"][1]
      facesIntercept[target,source] <- intercept
      facesPVal[target,source]      <- p
      dfResults[nrow(dfResults) + 1,] = list(source,target, "faces", "intercept", intercept )
      dfResults[nrow(dfResults) + 1,] = list(source,target, "faces", "p", p )
      if (p <= thres){
        dfResults[nrow(dfResults) + 1,] = list(source,target, "faces", "intercept_sig",paste(round(intercept,2),"*") )
      } else {
        dfResults[nrow(dfResults) + 1,] = list(source,target, "faces", "intercept_sig", paste(round(intercept,2),"") )
      }
      
      # create a name for the connection
      conName <- paste(regionNames[source],">",regionNames[target])
      dfFaces$Connection <- conName 
      bigDF <- rbind(bigDF,
                     subset(dfFaces, select = c("Subject","Parameter","Study","Hormone", "Connection")))
    }
  }
} 
print("Intercept =")
facesIntercept
print("p =")
facesPVal
```

### plot the connectivity matrix

```{r}
pHLM_b_emotions  <- qplot(x=Source , y=Target , data=subset(dfResults, Type == "intercept"), fill=as.numeric(Value), geom="tile") +
  geom_text(data=subset(dfResults, Type == "intercept_sig"), aes(label = Value, size = 35)) +
  scale_fill_gradient2(low = "blue", mid = "white", high = "red", midpoint=0, limits=colorRange) +
  scale_x_discrete(limits=c("OFA","FFA","STS")) +
  scale_y_discrete(limits=c("OFA","FFA","STS")) +
  myTheme +
  labs(title = "B-matrix\n(emotions)", x = "source region", y = "target region") + #tag = "B"
  coord_equal() +
  facet_grid()
pHLM_b_emotions
dev.copy(png,'/Users/roman/projects/coreSysRev/plots/HLM_BEmotions.png')
dev.off()
```

## histo

```{r}
# New facet label names for dose variable
study.labs <- c("study A","study B","study C","study D")
names(study.labs) <- c("0", "1", "2","3")

bigDF$Connection <- as.factor(bigDF$Connection)
pHist_b_emotions <- ggplot(bigDF) +
  geom_density(aes(x=Parameter), fill = "darkgrey") + 
  geom_vline(aes(xintercept=0)) + # vertical line at x = 0
  facet_grid(Study~Connection,
             labeller = labeller(Study = study.labs)) +
  labs(x = "parameter estimates", title = "B-matrix: emotions")
pHist_b_emotions
dev.copy(png,'/Users/roman/projects/coreSysRev/plots/Hist_BEmotions.png')
dev.off()
```
Show overview over the BMA parameters
```{r}
bigDF %>% split(.$Study) %>% map(summary)
```
## A matrix: context independent connections

### loop this over parameter

```{r}
# table for results
facesIntercept <- matrix(NA, 3, 3)
facesPVal      <- matrix(NA, 3, 3)
dfResults <- data.frame(Source=numeric(0), Target=numeric(0), Matrix=character(0), Type=character(0), Value=numeric(0), stringsAsFactors=FALSE)
bigDF <- data.frame(matrix(ncol=5,nrow=0, dimnames=list(NULL, c("Subject", "Parameter", "Study", "Hormone", "Connection"))))


for ( target in 1:3 ){      # target region
  for ( source in 1:3 ){    # source region
    if (source == target){
      next # skip this iteration if it is a self connection
    } else {
      
      # load parameters in df
      Parameter <-      c(dfEFP$mEpsA[target,source,], # DCM parameters
                          dfFEM$mEpsA[target,source,],
                          dfCYM$mEpsA[target,source,],
                          dfCYP$mEpsA[target,source,],
                          dfWaH$mEpsA[target,source,])
      Subject <- c(subNumEFP, subNumFEM, subNumCYM, subNumCYP, subNumWaH)
      Study <- c(rep(0,23),rep(1,27), rep(2,16+17), rep(3,123))
      Hormone <-  c(rep(0,23+27+16), rep(1,17), rep(0,123))
      dfFaces <- data.frame(Subject, Parameter, Study, Hormone)
      dfFaces$Subject <- as.factor(dfFaces$Subject)
      dfFaces$Study   <- as.factor(dfFaces$Study)
      dfFaces$Hormone <- as.factor(dfFaces$Hormone)
      
      # create contrasts
      dfFaces <- contrastCoding(df = dfFaces, colName = "Study", numLevels = 4, interceptCorrect = TRUE)
      
      # create hormone contrast
      dfFaces <- contrastCodingHormone(df = dfFaces, colName = "Hormone", numLevels = 2, interceptCorrect = TRUE)
      
      # estimate model
      m1 <- lme(Parameter ~ 1 + contrast_AvB + contrast_ABvC + contrast_ABCvD + contrast_MvP , random = ~1|Subject, data=dfFaces)

      # extract results
      intercept = m1$coefficients$fixed[1]
      p = summary(m1)$tTable[,"p-value"][1]
      facesIntercept[target,source] <- intercept
      facesPVal[target,source]      <- p
      dfResults[nrow(dfResults) + 1,] = list(source,target, "faces", "intercept", intercept )
      dfResults[nrow(dfResults) + 1,] = list(source,target, "faces", "p", p )
      if (p <= thres){
        dfResults[nrow(dfResults) + 1,] = list(source,target, "faces", "intercept_sig",paste(round(intercept,2),"*") )
      } else {
        dfResults[nrow(dfResults) + 1,] = list(source,target, "faces", "intercept_sig", paste(round(intercept,2),"") )
      }
      # create a name for the connection
      conName <- paste(regionNames[source],">",regionNames[target])
      dfFaces$Connection <- conName 
      bigDF <- rbind(bigDF,
                     subset(dfFaces, select = c("Subject","Parameter","Study","Hormone", "Connection")))
    }
  }
} 
print("Intercept =")
facesIntercept
print("p =")
facesPVal
```

### plot the connectivity matrix

```{r}
pHLM_a <- qplot(x=Source , y=Target , data=subset(dfResults, Type == "intercept"), fill=as.numeric(Value), geom="tile") +
  geom_text(data=subset(dfResults, Type == "intercept_sig"), aes(label = Value, size = 35)) +
  scale_fill_gradient2(low = "blue", mid = "white", high = "red", midpoint=0, limits=colorRange) +
  scale_x_discrete(limits=c("OFA","FFA","STS")) +
  scale_y_discrete(limits=c("OFA","FFA","STS")) +
  myTheme +
  labs(title = "A-matrix\n(context-independent)", x = "source region", y = "target region") + #tag = "B"
  coord_equal() +
  facet_grid()


pHLM_a
dev.copy(png,'/Users/roman/projects/coreSysRev/plots/HLM_A.png')
dev.off()
```

## histo

```{r}
# New facet label names for dose variable
study.labs <- c("study A","study B","study C","study D")
names(study.labs) <- c("0", "1", "2","3")

bigDF$Connection <- as.factor(bigDF$Connection)
pHist_a <- ggplot(bigDF) +
  geom_density(aes(x=Parameter), fill = "darkgrey") + 
  geom_vline(aes(xintercept=0)) + # vertical line at x = 0
  facet_grid(Study~Connection,
             labeller = labeller(Study = study.labs)) +
  labs(x = "parameter estimates", title = "A-matrix") +
  scale_x_continuous(breaks = seq(from = -1, to = 1, by = 1))
pHist_a
dev.copy(png,'/Users/roman/projects/coreSysRev/plots/Hist_A.png')
dev.off()
```
Show overview over the BMA parameters
```{r}
bigDF %>% split(.$Study) %>% map(summary)
```

## A matrix: self connections

### loop this over parameter

```{r}
# table for results
facesIntercept <- matrix(NA, 3, 3)
facesPVal      <- matrix(NA, 3, 3)
dfResults <- data.frame(Source=numeric(0), Target=numeric(0), Matrix=character(0), Type=character(0), Value=numeric(0), stringsAsFactors=FALSE)
bigDF <- data.frame(matrix(ncol=5,nrow=0, dimnames=list(NULL, c("Subject", "Parameter", "Study", "Hormone", "Connection"))))


for ( target in 1:3 ){      # target region
  for ( source in 1:3 ){    # source region
    if (source == target){

      
      # load parameters in df
      Parameter <-      c(dfEFP$mEpsA[target,source,], # DCM parameters
                          dfFEM$mEpsA[target,source,],
                          dfCYM$mEpsA[target,source,],
                          dfCYP$mEpsA[target,source,],
                          dfWaH$mEpsA[target,source,])
      
      Parameter <- - 0.5*exp(Parameter)
      
      Subject <- c(subNumEFP, subNumFEM, subNumCYM, subNumCYP, subNumWaH)
      Study <- c(rep(0,23),rep(1,27), rep(2,16+17), rep(3,123))
      Hormone <-  c(rep(0,23+27+16), rep(1,17), rep(0,123))
      dfFaces <- data.frame(Subject, Parameter, Study, Hormone)
      dfFaces$Subject <- as.factor(dfFaces$Subject)
      dfFaces$Study   <- as.factor(dfFaces$Study)
      dfFaces$Hormone <- as.factor(dfFaces$Hormone)
      
      # create contrasts
      dfFaces <- contrastCoding(df = dfFaces, colName = "Study", numLevels = 4, interceptCorrect = TRUE)
      
      # create hormone contrast
      dfFaces <- contrastCodingHormone(df = dfFaces, colName = "Hormone", numLevels = 2, interceptCorrect = TRUE)
      
      # estimate model
      m1 <- lme(Parameter ~ 1 + contrast_AvB + contrast_ABvC + contrast_ABCvD + contrast_MvP , random = ~1|Subject, data=dfFaces)

      # extract results
      intercept = m1$coefficients$fixed[1]
      p = summary(m1)$tTable[,"p-value"][1]
      facesIntercept[target,source] <- intercept
      facesPVal[target,source]      <- p
      dfResults[nrow(dfResults) + 1,] = list(source,target, "faces", "intercept", intercept )
      dfResults[nrow(dfResults) + 1,] = list(source,target, "faces", "p", p )
      if (p <= thres){
        dfResults[nrow(dfResults) + 1,] = list(source,target, "faces", "intercept_sig",paste(round(intercept,2),"*") )
      } else {
        dfResults[nrow(dfResults) + 1,] = list(source,target, "faces", "intercept_sig", paste(round(intercept,2),"") )
      }
      # create a name for the connection
      conName <- paste(regionNames[source],">",regionNames[target])
      dfFaces$Connection <- conName 
      bigDF <- rbind(bigDF,
                     subset(dfFaces, select = c("Subject","Parameter","Study","Hormone", "Connection")))
    } else {
        next # skip this iteration if it is NOT a self connection
    }
  }
} 
print("Intercept =")
facesIntercept
print("p =")
facesPVal
```

### plot the connectivity matrix

```{r}
pHLM_a <- qplot(x=Source , y=Target , data=subset(dfResults, Type == "intercept"), fill=as.numeric(Value), geom="tile") +
  geom_text(data=subset(dfResults, Type == "intercept_sig"), aes(label = Value, size = 35)) +
  scale_fill_gradient2(low = "blue", mid = "white", high = "red", midpoint=0, limits=colorRange) +
  scale_x_discrete(limits=c("OFA","FFA","STS")) +
  scale_y_discrete(limits=c("OFA","FFA","STS")) +
  myTheme +
  labs(title = "A-matrix\n(context-independent)", x = "source region", y = "target region") + #tag = "B"
  coord_equal() +
  facet_grid()


pHLM_a
dev.copy(png,'/Users/roman/projects/coreSysRev/plots/HLM_A_self.png')
dev.off()
```

## histo

```{r}
# New facet label names for dose variable
study.labs <- c("study A","study B","study C","study D")
names(study.labs) <- c("0", "1", "2","3")

bigDF$Connection <- as.factor(bigDF$Connection)
pHist_a <- ggplot(bigDF) +
  geom_density(aes(x=Parameter), fill = "darkgrey") + 
  geom_vline(aes(xintercept=0)) + # vertical line at x = 0
  facet_grid(Study~Connection,
             labeller = labeller(Study = study.labs)) +
  labs(x = "parameter estimates", title = "A-matrix: self-connections") +
  scale_x_continuous(breaks = seq(from = -1, to = 1, by = 1))
pHist_a
dev.copy(png,'/Users/roman/projects/coreSysRev/plots/Hist_A_self.png')
dev.off()
```
Show overview over the BMA parameters
```{r}
bigDF %>% split(.$Study) %>% map(summary)
```





## B matrix: effect of fame

### loop this over parameter

```{r}
# table for results
facesIntercept <- matrix(NA, 3, 3)
facesPVal      <- matrix(NA, 3, 3)
dfResults <- data.frame(Source=numeric(0), Target=numeric(0), Matrix=character(0), Type=character(0), Value=numeric(0), stringsAsFactors=FALSE)
bigDF <- data.frame(matrix(ncol=5,nrow=0, dimnames=list(NULL, c("Subject", "Parameter", "Study", "Hormone", "Connection"))))


for ( target in 1:3 ){      # target region
  for ( source in 1:3 ){    # source region
    if (source == target){
      next # skip this iteration if it is a self connection
    } else {
      
      
      Subject <- c(subNumWaH)
      Study <- c(rep(3,123))
      
      # load parameters in df
      Parameter <-      c(dfWaH$mEpsBFame[target,source,]) # DCM parameters
                          
      dfFaces <- data.frame(Subject, Parameter, Study)
      dfFaces$Subject <- as.factor(dfFaces$Subject)
      dfFaces$Study   <- as.factor(dfFaces$Study)

      # create contrasts
      #dfFaces <- contrastCoding(df = dfFaces, colName = "Study", numLevels = 2, interceptCorrect = TRUE)
      
      # estimate model
      m1 <- lme(Parameter ~ 1, random = ~1|Subject, data=dfFaces)

      # extract results
      intercept = m1$coefficients$fixed[1]
      p = summary(m1)$tTable[,"p-value"][1]
      facesIntercept[target,source] <- intercept
      facesPVal[target,source]      <- p
      dfResults[nrow(dfResults) + 1,] = list(source,target, "faces", "intercept", intercept )
      dfResults[nrow(dfResults) + 1,] = list(source,target, "faces", "p", p )
      if (p <= thres){
        dfResults[nrow(dfResults) + 1,] = list(source,target, "faces", "intercept_sig",paste(round(intercept,2),"*") )
      } else {
        dfResults[nrow(dfResults) + 1,] = list(source,target, "faces", "intercept_sig", paste(round(intercept,2),"") )
      }
      # create a name for the connection
      conName <- paste(regionNames[source],">",regionNames[target])
      dfFaces$Connection <- conName 
      bigDF <- rbind(bigDF,
                     subset(dfFaces, select = c("Subject","Parameter", "Connection","Study")))
      }
    
    
  }
} 
print("Intercept =")
facesIntercept
print("p =")
facesPVal
```

### plot the connectivity matrix

```{r}
pHLM_B_fame <- qplot(x=Source , y=Target , data=subset(dfResults, Type == "intercept"), fill=as.numeric(Value), geom="tile") +
  geom_text(data=subset(dfResults, Type == "intercept_sig"), aes(label = Value, size = 35)) +
  scale_fill_gradient2(low = "blue", mid = "white", high = "red", midpoint=0, limits=colorRange) +
  scale_x_discrete(limits=c("OFA","FFA","STS")) +
  scale_y_discrete(limits=c("OFA","FFA","STS")) +
  myTheme +
  labs(title = "B-matrix\n(fame)", x = "source region", y = "target region") + #tag = "B"
  coord_equal() +
  facet_grid()

pHLM_B_fame
dev.copy(png,'/Users/roman/projects/coreSysRev/plots/HLM_Bfame.png')
dev.off()
```


## histo

```{r}
# New facet label names for dose variable
study.labs <- c("study A","study B","study C","study D")
names(study.labs) <- c("0", "1", "2","3")

bigDF$Connection <- as.factor(bigDF$Connection)
pHist_B_fame <- ggplot(bigDF) +
  geom_density(aes(x=Parameter), fill = "darkgrey") + 
  geom_vline(aes(xintercept=0)) + # vertical line at x = 0
  facet_grid(Study~Connection,
             labeller = labeller(Study = study.labs)) +
  labs(x = "parameter estimates", title = "B-matrix: fame") +
  scale_x_continuous(breaks = seq(from = -4, to = 4, by = 2))
pHist_B_fame
dev.copy(png,'/Users/roman/projects/coreSysRev/plots/Hist_Bfame.png')
dev.off()
```
Show overview over the BMA parameters
```{r}
bigDF %>% split(.$Study) %>% map(summary)
```

## C matrix: driving input

### loop this over parameter

```{r}
# table for results
facesIntercept <- matrix(NA, 1, 1)
facesPVal      <- matrix(NA, , 1)
dfResults <- data.frame(Source=numeric(0), Target=numeric(0), Matrix=character(0), Type=character(0), Value=numeric(0), stringsAsFactors=FALSE)
bigDF <- data.frame(matrix(ncol=5,nrow=0, dimnames=list(NULL, c("Subject", "Parameter", "Study", "Hormone", "Connection"))))


target = 1
source = 1

Parameter <-      c(dfEFP$mEpsC[target,source,], # DCM parameters
                    dfFEM$mEpsC[target,source,],
                    dfCYM$mEpsC[target,source,],
                    dfCYP$mEpsC[target,source,],
                    dfWaH$mEpsC[target,source,])
Subject <- c(subNumEFP, subNumFEM, subNumCYM, subNumCYP, subNumWaH)
Study <- c(rep(0,23),rep(1,27), rep(2,16+17), rep(3,123))
Hormone <-  c(rep(0,23+27+16), rep(1,17), rep(0,123))

dfFaces <- data.frame(Subject, Parameter, Study, Hormone)
dfFaces$Subject <- as.factor(dfFaces$Subject)
dfFaces$Study   <- as.factor(dfFaces$Study)
dfFaces$Hormone   <- as.factor(dfFaces$Hormone)


# create contrasts
dfFaces <- contrastCoding(df = dfFaces, colName = "Study", numLevels = 4, interceptCorrect = TRUE)

# create hormone contrast
dfFaces <- contrastCodingHormone(df = dfFaces, colName = "Hormone", numLevels = 2, interceptCorrect = TRUE)
      
      
# estimate model
m1 <- lme(Parameter ~ 1 + contrast_AvB + contrast_ABvC + contrast_ABCvD + contrast_MvP , random = ~1|Subject, data=dfFaces)

# extract results
intercept = m1$coefficients$fixed[1]
p = summary(m1)$tTable[,"p-value"][1]
facesIntercept[target,source] <- intercept
facesPVal[target,source]      <- p
dfResults[nrow(dfResults) + 1,] = list(source,target, "faces", "intercept", intercept )
dfResults[nrow(dfResults) + 1,] = list(source,target, "faces", "p", p )

if (p <= thres){
  dfResults[nrow(dfResults) + 1,] = list(source,target, "faces", "intercept_sig",paste(round(intercept,2),"*") )
} else {
  dfResults[nrow(dfResults) + 1,] = list(source,target, "faces", "intercept_sig", paste(round(intercept,2),"") )
}

bigDF <- dfFaces
#rbind(bigDF,
#               subset(dfFaces, select = c("Subject","Parameter","Study","Hormone","Connection")))

print(paste("Intercept =", facesIntercept))
print(paste("p =", facesPVal))


```

### plot the connectivity matrix

```{r}
myTheme$legend.position = "right" # add this to myTheme, to have a color-legend in this plot
#myTheme <- theme(
#    panel.grid.major = element_blank(), 
#    panel.grid.minor = element_blank(),
#    panel.background = element_rect(fill = "transparent",colour = NA),
#    plot.background = element_rect(fill = "transparent",colour = NA),
#    axis.text.x = element_text(color="black", # x tick labels
#                           size=10, angle=0),
#    axis.text.y = element_text(color="black", # y tick labels
#                           size=10, angle=0),
#    panel.border = element_blank(),
#    legend.position = "right"
#    )
pHLM_c <- qplot(x=Source , y=Target , data=subset(dfResults, Type == "intercept"), fill=as.numeric(Value), geom="tile") +
  geom_text(data=subset(dfResults, Type == "intercept_sig"), aes(label = Value)) +
  scale_fill_gradient2(low = "blue", mid = "white", high = "red", midpoint=0, limits=c(-1.5,1.5)) +
  scale_x_discrete(limits=c("faces")) +
  scale_y_discrete(limits=c("OFA")) +
  myTheme +
  coord_equal() +
  labs(title = "C-matrix", x = "input", y = "target region",
       fill = "parameter estimate")
  facet_grid()
  
  
pHLM_c
dev.copy(png,'/Users/roman/projects/coreSysRev/plots/HLM_C.png')
dev.off()
```
## histo

```{r}
# New facet label names for dose variable
study.labs <- c("study A","study B","study C","study D")
names(study.labs) <- c("0", "1", "2","3")

#bigDF$Connection <- as.factor(bigDF$Connection)
pHist_c <- ggplot(bigDF) +
  geom_density(aes(x=Parameter), fill = "darkgrey") + 
  geom_vline(aes(xintercept=0)) + # vertical line at x = 0
  facet_grid(Study~.,
             labeller = labeller(Study = study.labs)) +
  labs(x = "parameter estimates", title = "C-matrix")
pHist_c
dev.copy(png,'/Users/roman/projects/coreSysRev/plots/Hist_C.png')
dev.off()

```

Show overview over the BMA parameters
```{r}
bigDF %>% split(.$Study) %>% map(summary)
```



# plot a grid with BMA results
## A and C Matrix


```{r}
library(gridExtra)

layoutMat <- rbind(c(1,1,1,1,2),
                   c(1,1,1,1,2))
grid.arrange(pHist_a,
               #pHist_b_faces,
               #pHist_b_emotions,
               #pHist_B_fame,
               pHist_c,
             layout_matrix = layoutMat) #title = "C-matrix"
dev.copy(png,'/Users/roman/projects/coreSysRev/plots/Density_AC.png')
dev.off()

```

## B Matrix

```{r}
layoutMat <- rbind(c(1))
grid.arrange(pHist_b_faces,
             layout_matrix = layoutMat)
dev.copy(png,'/Users/roman/projects/coreSysRev/plots/Density_B-faces.png')
dev.off()

```


```{r}
layoutMat <- rbind(c(1),
                   c(1),
                   c(2))
grid.arrange(pHist_b_emotions,
             pHist_B_fame,
             layout_matrix = layoutMat)
dev.copy(png,'/Users/roman/projects/coreSysRev/plots/density_B-emotions_B-fame.png')
dev.off()

```



# plot a grid with HLM results



```{r}
library(gridExtra)
                      
layoutMat <- rbind(c(1,1,2,2),
                   c(1,1,2,2),
                   c(3,3,4,4),
                   c(3,3,4,4),
                   c(NA,5,5,NA),
                   c(NA,5,5,NA))

tiff('/Users/roman/projects/coreSysRev/plots/HLM_ABBC.png',width = 8, height = 12, units = "in", res = 1000)  
grid.arrange(pHLM_a,
             pHLM_b_faces,
             pHLM_b_emotions,
             pHLM_B_fame, 
             pHLM_c,
             layout_matrix = layoutMat)
#dev.copy(png,'/Users/roman/projects/coreSysRev/plots/HLM_ABBC.png')
dev.off()
```


